% Template PNSAC newsletter - Article
% Language: Latex
%

% Head

\title{North Star Merchandise}
\author{Phil Chrysler}

\maketitle

\end{multicols}

The idea for North Star merchandise started with a need to identify those volunteers that were assisting when the aircraft was put on display to the general public.  That requirement evolved into the blue member's only crested golf shirts (men and ladies).  Over time we have added baseball caps, toques sweatshirts, T-shirts and fleece vests (by special order) all with the North Star crest.  Also a 1:200 scale model of the aircraft was produced in limited numbers of which we still have a few.  With the exception of the members only golf shirt all the other items are available at the Aviation and Space Museum store.  The items are available to members of the North Star directly at a discount. 
 
We also have a CD of the North Star operating manual and a North Star pin that are not available in the Museum store.

From the beginning our purpose was to bring more awareness to the general public of our restoration activities rather generate money on the sale of the items.  So we have made an effort to keep the quality high and profits modest.  All money earned is used to advance the restoration effort.  The North Star web site has prices and pictures of the available items.

Merchandise page: {\normalfont\color{blue}\texttt{\url{http://www.projectnorthstar.ca/menu-merchanidise}}}

\begin{footnotesize}
    \raggedleft PNSAC\\
\end{footnotesize}

\begin{multicols}{2}

% End of text.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main_document.tex
%%% End: 

