% Template PNSAC newsletter - Article
% Language: Latex
%

% Head

\title{Message from the CASM Director General}
%\subtitle{November 2015}
\author{Chris Kitzan}

\maketitle

\begin{quotation}
	\textit{Chris Kitzan was appointed the new director general of CASM last
	November. Previously he was the chief of staff at Library and Archives
	Canada. Before that he worked as a curator and exhibit manager at what
	was then known as the Canadian Museum of Civilization.}
\end{quotation}


My tenure at the Museum is just beginning, but already I have observed
first-hand the contribution volunteers are making, from my meetings
with members, to my perspective as a father watching you
enthusiastically cater to my eight year old son's interests, to the
communications I have received from you with ideas and offers of
support, and finally from guests who have written thanking the Museum
for experiences they have had interacting with you on the floor.  I
have never worked in an organization that had so many individuals
willing to donate anywhere near the amount of time and energy you do.
Given that, is it fair to want more?  I hope so.  With your support, I
would like to tap a little deeper into your energy and discuss ways we
can further work together to innovate and inspire.  

I recognize that increased collaboration between passionate parties
will sometimes create moments of turbulence.  I feel it is a small
price to pay if we are all committed to the ultimate goal --
maximizing the potential of this organization.  That is why, on the
North Star front, Richard and CASM staff are currently trying to find
solutions that allow us to meet our collective objectives.  And why I
hope that these initial conversations lead to increased discussions,
and volunteer/staff collaboration on a wider range of fronts.  

On the one hand, the Canadair North Star was a reliable, versatile
Canadian aircraft that provided our country with excellent service on
both the military and civilian fronts for decades.  On the other, it
made such a bloody racket that wherever it went it could not be
ignored.  To my mind it's a worthy symbol of the kind of Museum I
would like to see us continue to develop.  Based on its collection,
its staff and its volunteers CASM has already established a reputation
as a world-class Museum.    That standard cannot be sacrificed.  At
the same time, there is room for us to make more noise; to try new
ways to reach Canadians, catch their attention, and further share our
rich collection and stories with them. 

\begin{footnotesize}
  \raggedleft PNSAC\\
\end{footnotesize}

% End of text.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main_document.tex
%%% End: 

