% Template PNSAC newsletter - Article
% Language: Latex
%

% Head

\title{Notes from the President}
\author{Richard Lodge}

\maketitle

As I write these notes in the middle of April, I see a fresh fall of
snow on the ground.  For the first time in many years, the North Star,
already out in the open, will be covered in snow.  This unusual
situation has been caused by the Star Wars exhibition to be located in
the Storage Hangar this summer.  The larger Argus airplane has also
been moved outside, in a position which reduces visibility of the
North Star for the public.  This will present a challenge to us in
showing off our work to Museum visitors.

The Star Wars exhibition has also affected our plans for commemorating
the 10th anniversary of the founding of the Project North Star
Association.  We are now planning to celebrate the anniversary when we
open the North Star for the public on Canada Day.  That will be the
only time this summer when we can invite the general public to see the
North Star and offer our members conducted tours inside the plane.  We
will ensure that there are good directions to the North Star and
volunteers located in the main Museum will assist visitors and members
in finding it.

All this has had only a minor effect on the plane restoration.  We are
very actively working both inside the restoration shop and inside the
plane itself.  As usual our Project Manager has provided elsewhere in
the Chronicle a comprehensive report of our progress.

In the next Chronicle, we are planning to start a Letters to the
Editor section.  Many of our members are not located in Ottawa and may
well have interesting questions or comments on our work, or stories or
pictures about North Star in general.  We will welcome any letters or
stories, which should be sent to the Editor
(\email{editor@projectnorthstar.ca}) by email or by mail to the
address shown on the last page of this newsletter.  As with any
publication, our editor will decide whether an item should be
published.


\begin{footnotesize}
    \raggedleft PNSAC\\
\end{footnotesize}

% End of text.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main_document.tex
%%% End: 

